Faithful Variable Screening for\\ High-Dimensional Convex Regression

### 2014-10-17 tex/scam/appendix.tex
new plots

By additive faithfulness of the ACDC procedure, it is necessary that $f^*_k \neq 0$ or $g^*_k \neq 0$ for all $k \in S$. \\

Intuitively, we would like to show the following:
\begin{align*}
\| f_0 - \hat{f} \|_P & \approx \| f_0 - f^* \|_P \\
\| f_0 - f^* - \hat{g}_k \|_P & \approx \| f_0 - f^* - g^*_k \|_P 
       \quad \trm{for all $k \in S$ where $f^*_k = 0$}
\end{align*}
where the estimation error is a term that decreases with $n$.

Suppose $\hat{f}_k = 0$ and $f^*_k \neq 0$, then, when $n$ is large enough, there must exist a contradiction because the population risk of $f^*$, $\| f_0 - f^* \|_P$, is strictly larger than the population risk of the best approximation whose $k$-th component is constrained to be zero.

@@

>>>>

By additive faithfulness of the AC/DC procedure, it is known that $f^*_k \neq 0$ or $g^*_k \neq 0$ for all $k \in S$. \\

Intuitively, we would like to show that the risks of the AC/DC estimators $\hat{f}, \hat{g}$ tends to the risks of the population optimal functions $f^*, g^*$:
\begin{align*}
\| f_0 - \hat{f} \|^2_P & = \| f_0 - f^* \|^2_P + \trm{err}_+(n) \\
\| f_0 - f^* - \hat{g}_k \|^2_P &=  \| f_0 - f^* - g^*_k \|^2_P + \trm{err}_-(n) 
       \quad \trm{for all $k \in S$ where $f^*_k = 0$}
\end{align*}
where the estimation errors $\trm{err}_+(n), \trm{err}_-(n)$ decrease with $n$ at some rate.

Suppose $\hat{f}_k = 0$ and $f^*_k \neq 0$, then, when $n$ is large enough such that $\trm{err}_+(n)$ and $\trm{err}_-(n)$ are smaller than $\alpha_+, \alpha_-$ (defined in equation~\ref{eqn:signal_level_defn}), there must exist a contradiction because the risk of $f^*$, $\| f_0 - f^* \|_P$, is strictly larger by $\alpha_+$ than the risk of the best approximation whose $k$-th component is constrained to be zero.

@@

Theorem~\ref{thm:convex_consistent} and theorem~\ref{thm:concave_consistent} characterize $\trm{err}_+(n)$ and $\trm{err}_-(n)$ respectively.

### 2014-10-17 tex/scam/experiments.tex
new plots

\section{Experiments}
\label{sec:thesims}
%\subsection{Simulations}
We first illustrate our methods using a simulation of the model
\begin{equation}\nonumber
         Y_i = \x_{iS}^{\top}\Q\x_{iS} + \epsilon_i \quad (i=1,2,\ldots,n).
\end{equation}
Here $\x_{i}$ denotes data sample $i$ drawn from $\mathcal{N}(\bds{0},\bds{I}_{p})$, 
$\x_{iS}$ is a subset of $\x_i$ with dimension $|S|=5$, where $S$
represents the relevant variable set, and 
$\epsilon_i$ is additive noise drawn from $\mathcal{N}(0,1)$. 
The matrix $\Q$ is a symmetric positive definite matrix of dimension $|S|\times{}|S|$. 
Note that if $\Q$ is diagonal, then the true function is convex
additive; 
otherwise the true function is convex but not additive.
For all simulations in this section, we set $\lambda=4\sqrt{{\log(np)}/{n}}$.

In the first simulation, we set $\Q=\bds{I}_{|S|}$ (the additive
case), and choose $n=100, 200,\ldots,1000$ and $p=64,128,256$ and $512$.
For each $(n,p)$ combination, we generate $200$ independent data
sets. For each data set we use the AC/DC algorithm to estimate the model support.
We plot the probability of
support recovery over the $200$ data sets in Figure \ref{Support}(a).  We
observe that the algorithm performs consistent variable selection when the true
function is convex additive.    To give the reader a
sense of the running speed, for a 
data set with $n=1000$ and $p=512$, the code runs in roughly two 
minutes on a machine with 2.3 GHz Intel Core i5 CPU and 4 GB memory.

In the second simulation, we study the case in which the true function
is convex but not additive. We generate four $\Q$ matrices
plotted in Figure \ref{Support}(b), where the diagonal elements are all one and
the off-diagonal elements are $\frac{1}{2}$ with probability $\alpha$
($\alpha=0,0.2,0.5,1$ for the four cases). We fix $p=128$ and choose
$n=100,200,\ldots,1000$. We again run the AC/DC optimization on $200$
independently generated data sets and plot the probability of recovery
in Figure \ref{Support}(c). The results demonstrate that AC/DC performs
consistent variable selection even if the true function is not additive (but
still convex).

In the third simulation, we study the case of a correlated design, where
$\x_i$ is drawn from $\mathcal{N}(\bds{0},\bds{\Sigma})$
instead of $\mathcal{N}(\bds{0},\bds{I}_{p})$, with
$\Sigma_{ij}=\nu^{|i-j|}$. We use the non-additive $\Q$ with
$\alpha=0.5$ and fix $p=128$.  The recovery curves for $\nu=0.2, 0.4,
0.6, 0.8$ are shown in Figure \ref{Support}(d). As can be seen, for
design of moderate correlation, AC/DC can still select relevant
variables well.

@@

We first use all $n=506$ samples (with normalization) to fit AC/DC,
using a set of candidate regularization parameters $\{\lambda^{(t)}\}$
with $\lambda^{(1)}=0$ (no regularization). For each $\lambda^{(t)}$
we obtain a subgradient matrix $\bds{\beta}^{(t)}$ with $p=13$
rows. The non-zero rows in this matrix indicate the variables selected
using $\lambda^{(t)}$.  We plot $\|\bds{\beta}^{(t)}\|_{\infty}$ and
the row-wise mean of $\bds{\beta}^{(t)}$ versus the normalized norm
$\frac{\|\bds{\beta}^{(t)}\|_{\infty,1}}{\|\bds{\beta}^{(1)}\|_{\infty,1}}$
in Figures \ref{Boston}(a) and \ref{Boston}(b).  For comparison, we
plot the LASSO/LARS result in a similar way in Figure \ref{Boston}(c).
From the figures we observe that the first three variables selected by
AC/DC and LASSO are the same: \tts{LSTAT}, \tts{RM} and \tts{PTRATIO},
consistent with previous findings~\citep{SpAM:07}.  The fourth
variable selected by AC/DC is \tts{TAX} (with $\lambda^{(t)}=0.09$).
We then refit AC/DC with only these four variables without
regularization, and plot the estimated additive functions in Figure
\ref{Boston}(e). As can be seen, these functions contain clear
nonlinear effects which cannot be captured by LASSO. The shapes of
these functions are in agreement with those obtained by
SpAM~\citep{SpAM:07}.

@@

\begin{center}
\begin{tabular}{ccc}
\hskip-10pt
  \includegraphics[width=.35\textwidth]{figs/Additive} &
\hskip-25pt
  \includegraphics[width=.35\textwidth]{figs/Additive1} &
\hskip-25pt
  \includegraphics[width=.35\textwidth]{figs/LASSO} 
\\
\hskip-10pt 
AC/DC $\|\beta_k\|_\infty$ paths & 
\hskip-25pt 
AC/DC $\text{mean}(\beta_k)$ paths &
\hskip-25pt
LASSO $\beta_k$ paths
\end{tabular}
\begin{tabular}{cc}
  \includegraphics[width=.37\textwidth]{figs/MSE} &
  \includegraphics[width=.43\textwidth]{figs/Convex}
\\
predictive MSE & estimated functions from AC/DC
\end{tabular}
\end{center}
\caption{Results on Boston housing data, showing regularization paths,
 MSE and fitted functions.}\label{Boston}
\end{figure*}

>>>>

\section{Experiments}
\label{sec:thesims}
%\subsection{Simulations}
We first illustrate our methods using a simulation of the model
\begin{equation}\nonumber
         Y_i = \x_{iS}^{\top}\Q\x_{iS} + \epsilon_i \quad (i=1,2,\ldots,n).
\end{equation}
Here $\x_{i}$ denotes data sample $i$ drawn from $\mathcal{N}(\bds{0}, \Sigma)$, 
$\x_{iS}$ is a subset of $\x_i$ with dimension $|S|=5$, where $S$
represents the relevant variable set, and 
$\epsilon_i$ is additive noise drawn from $\mathcal{N}(0,1)$. 
The matrix $\Q$ is a symmetric positive definite matrix of dimension $|S|\times{}|S|$. 
Note that if $\Q$ is diagonal, then the true function is convex
additive; 
otherwise the true function is convex but not additive.
For all simulations in this section, we set $\lambda=4\sqrt{{\log(np)}/{n}}$.

In the first simulation, we vary the ambient dimension $p$. We set $Q$ as one on the diagonal and $1/2$ on the off-diagonal with $0.5$ probability, and choose $n=100, 200,\ldots,1000$ and $p=64,128,256$ and $512$. We use independent design by setting $\Sigma = Id$.
For each $(n,p)$ combination, we generate $100$ independent data
sets. For each data set we use the AC/DC algorithm to estimate the model support.
We plot the probability of
support recovery over the $100$ data sets in Figure \ref{Support}(a).  We
observe that the algorithm performs consistent variable selection even if the dimensionality is large. To give the reader a
sense of the running speed, for a 
data set with $n=1000$ and $p=512$, the code runs in roughly two 
minutes on a machine with 2.3 GHz Intel Core i5 CPU and 4 GB memory.

In the second simulation, we vary the sparsity of the $Q$ matrix, that is, we vary the extent to which the true function is non-additive. We generate four $\Q$ matrices
plotted in Figure \ref{Support}(b), where the diagonal elements are all one and
the off-diagonal elements are $\frac{1}{2}$ with probability $\alpha$
($\alpha=0,0.2,0.5,1$ for the four cases). We fix $p=128$ and choose
$n=100,200,\ldots,1000$. We use independent design by seting $\Sigma = Id$. We again run the AC/DC optimization on $100$
independently generated data sets and plot the probability of recovery
in Figure \ref{Support}(c). The results demonstrate that AC/DC performs
consistent variable selection even if the true function is not additive (but
still convex).

In the third simulation, we use correlated design and vary the correlation. We let
$\x_i$ be drawn from $\mathcal{N}(\bds{0},\bds{\Sigma})$
instead of $\mathcal{N}(\bds{0},\bds{I}_{p})$, with
$\Sigma_{ij}=\nu^{|i-j|}$. We use the non-additive $\Q$ with
$\alpha=0.5$ and fix $p=128$.  The recovery curves for $\nu=0.2, 0.4,
0.6, 0.8$ are shown in Figure \ref{Support}(d). As can be seen, for
design of moderate correlation, AC/DC can still select relevant
variables well.

@@

We first use all $n=506$ samples (with normalization) to fit AC/DC,
using a set of candidate regularization parameters $\{\lambda^{(t)}\}$
with $\lambda^{(1)}=0$ (no regularization). For each $\lambda^{(t)}$
we obtain a function value matrix $\bds{h}^{(t)}$ with $p=13$
rows. The non-zero rows in this matrix indicate the variables selected
using $\lambda^{(t)}$.  We plot $\|\bds{h}^{(t)}\|_{\infty}$ and
the row-wise mean of $\bds{h}^{(t)}$ versus the normalized norm
$\frac{\|\bds{h}^{(t)}\|_{\infty,1}}{\|\bds{h}^{(1)}\|_{\infty,1}}$
in Figures \ref{Boston}(a) and \ref{Boston}(b).  For comparison, we
plot the LASSO/LARS result in a similar way in Figure \ref{Boston}(c).
From the figures we observe that the first three variables selected by
AC/DC and LASSO are the same: \tts{LSTAT}, \tts{RM} and \tts{PTRATIO},
consistent with previous findings~\citep{SpAM:07}.  The fourth
variable selected by AC/DC is \tts{INDUS} (with $\lambda^{(t)}=0.7$).
We then refit AC/DC with only these four variables without
regularization, and plot the estimated additive functions in Figure
\ref{Boston}(e). As can be seen, these functions contain clear
nonlinear effects which cannot be captured by LASSO. The shapes of
these functions are in agreement with those obtained by
SpAM~\citep{SpAM:07}.

@@

\begin{center}
\begin{tabular}{cc}
%\hskip-10pt
  \includegraphics[width=.37\textwidth]{figs/acdc_path} &
%\hskip-25pt
  \includegraphics[width=.37\textwidth]{figs/lasso_path} 
\\
%\hskip-10pt 
AC/DC $\|f_k\|_\infty$ paths & 
%\hskip-25pt
LASSO $|\beta_k|$ paths \\
%\end{tabular}
%\begin{tabular}{cc}
  \includegraphics[width=.37\textwidth]{figs/MSEacdc} &
  \includegraphics[width=.43\textwidth]{figs/acdc_functs}
\\
predictive MSE & estimated functions from AC/DC
\end{tabular}
\end{center}
\caption{Results on Boston housing data, showing regularization paths,
 MSE and fitted functions.}\label{Boston}
\end{figure*}

### 2014-10-17 tex/scam/sparsistency.tex
new plots

Theorem~\ref{thm:deterministic} allows us to separately analyze the false negative
rates and false positive rates. To control false positives,
we analyze the condition on $\lambda_n$ for $k \in S^c$. To control
false negatives, we analyze the restricted regression.

@@

Let $\mathcal{C}^1$ denote the set of univariate convex functions
supported on $[-b,b]$, 
and let  $\mathcal{C}_1^{p}$ denote the set of convex additive functions
$\mathcal{C}_1^p \equiv \{ f \,:\, f = \sum_{k=1}^p f_k, \,
   f_k \in \mathcal{C}^1 \} $.  
Let $f^*(\mathbf{x}) = \sum_{k=1}^p f^*_k(x_k)$ be the population risk
minimizer in $\mathcal{C}_1^p$, 
\begin{equation}
f^* \equiv \arg\min_{f \in \mathcal{C}_1^p} \E\big(f_0(X) - f^*(X)
\big)^2.
\end{equation}
Similarly, we define $\mh \mathcal{C}^1$ as the set of univariate concave functions supported on $[-b, b]$ and define
\begin{equation}
g^*_k = \arg\min_{g_k \in \mh \mathcal{C}^1} \E \big( f_0(X) - f^*(X)
- g_k(X_k) \big)^2.
\end{equation}
We let $S = \{ k = 1,\ldots,p \,:\, f^*_k \neq 0 \trm{ or } g^*_k \neq 0\}$. By additive faithfulness (Theorem~\ref{thm:acdc_faithful}), it must be that $S_0 \subset S$. 
Each of our theorems will use a subset of the following assumptions:
\begin{packed_enum}
\item[A1:] $X_S, X_{S^c}$ are independent. 
\item[A2:] $f_0$ is convex and twice-differentiable. 
\item[A3:] $\|f_0\|_\infty \leq sB$ and $\| f^*_k \|_\infty \leq B$ for all $k$.
\item[A4:] $W$ is mean-zero sub-Gaussian, independent of $X$, with scale $\sigma$; i.e., for all $t \in \R$, $\E e^{t \epsilon} \leq e^{\sigma^2 t^2 / 2}$.
\end{packed_enum}
By assumption A1, $f^*_k$ is must be zero for $k\notin S$.
We define $\alpha_{+}, \alpha_{-}$ as a measure of the signal strength of the weakest variable:
\begin{align*}
\alpha_{+} &= \inf_{f \in \mathcal{C}_1^p \,:\, \exists k ,\, f^*_k \neq 0 \,\wedge\, f_k = 0} 
       \Big\{ \mathbb{E} \big( f_0(X) - f(X) \big)^2 - 
        \mathbb{E} \big( f_0(X) - f^*(X) \big)^2  \Big\}\\
\alpha_{-} &=   \min_{k \in S \,:\, g^*_k \neq 0}
      \Big\{ \mathbb{E} \big( f_0(X) - f^*(X) \big)^2 - 
    \mathbb{E} \big( f_0(X) - f^*(X) - g^*_k(X_k) \big)^2 \Big\}
\end{align*}
These quantities play the role of the absolute value of the smallest nonzero
coefficient in the true linear model in lasso theory.  Intuitively, if
$\alpha_{+}$ is small, then it is easier to make a false omission in the
additive convex stage of the procedure. If $\alpha_{-}$ is small, then
it is easier to make a false omission in the decoupled concave stage
of the procedure.

@@

\begin{theorem}[Controlling false positives]
\label{thm:false_positive}
Suppose assumptions A1-A4 hold. Define $\tilde{\sigma} \equiv \max(\sigma, B)$,
and suppose 
\begin{equation}
\lambda_n \geq 8 s_0 \tilde{\sigma}  \sqrt{ \frac{\log^2 np}{n}}.
\end{equation}  
Then with probability at least $ 1 - \frac{12}{np}$, for all $k \in
S^c$, and for all $i'=1,\ldots, n$,
\begin{equation}
\Big| \frac{1}{2n}\hat{r}^\tran \mathbf{1}_{(i':n)_k} \Big| < \lambda_n
\end{equation}
and for all $k \in S^c$, both the AC solution $\hat{f}_k$ from optimization~\eqref{opt:alternate_opt} and the DC solution $\hat{g}_k$ from optimization~\eqref{opt:alternate_opt_concave} are zero. 
\end{theorem}

@@

\begin{theorem}[Controlling false negatives]
\label{thm:false_negative}
Suppose assumptions A1-A4 hold. Let $\hat{f}$ be any AC solution to
the restricted regression with $B$-boundedness constraint, and let
$\hat{g}_k$ be any DC solution to the restricted regression with
$B$-boundedness constraint. Let $\tilde{\sigma}$ denote $\max(\sigma,
B)$.  Suppose 
\begin{equation}
\lambda_n \leq 9 s_0 \tilde{\sigma} \sqrt{\frac{1}{n} \log^2 np}
\end{equation}
and that $n$ is sufficiently large so that 
\begin{equation}
\frac{n^{4/5}}{\log np} \geq B^4 \tilde{\sigma}^2 s_0^5.
\end{equation}
Assume that the signal-to-noise ratio satisfies
\begin{align}
\frac{\alpha_{+}}{\tilde{\sigma}} & \geq c B^2
\sqrt{\frac{s_0^5}{n^{4/5}} \log^2 np}\\
\frac{\alpha_{-}^2}{\tilde{\sigma}} &\geq c B^2
\sqrt{\frac{s_0^5}{n^{4/5}} \log^2 np}
\end{align}
where $c$ is a constant.  Then with probability at least $1 -
\frac{C}{n}$ for some constant $C$, 
$\hat{f}_k \neq 0$ or $\hat{g}_k \neq 0$ 
for all $k \in S$.
\end{theorem}

This is a finite sample version of
Theorem~\ref{thm:convex_faithful}. We need stronger assumptions in
Theorem~\ref{thm:false_negative} to use our additive faithfulness
result, Theorem~\ref{thm:convex_faithful}. We also include an extra
boundedness constraint so that we can use recent bracketing number
results \cite{kim2014global}.

@@

\end{corollary}
The above corollary implies that sparsistency is achievable at the
same exponential scaling of the ambient dimension scaling attained
with parametric models, $p = O(\exp(n^c))$ for $c<1$.  The cost of
nonparametric modeling through shape constraints 
is reflected in the scaling with respect to
the number of relevant variables, which can scale as $s_0 = o(n^{4/25})$.

>>>>

Theorem~\ref{thm:deterministic} allows us to separately analyze the false negative
rates and false positive rates. To control false positives,
we analyze the condition on $\lambda_n$ for $k \in S^c$. To control
false negatives, we need only analyze the restricted regression with only $|S|$ variables.

@@

Let $\mathcal{C}^1$ denote the set of univariate convex functions
supported on $[-b,b]$, 
and let  $\mathcal{C}_1^{p}$ denote the set of convex additive functions
$\mathcal{C}_1^p \equiv \{ f \,:\, f = \sum_{k=1}^p f_k, \,
   f_k \in \mathcal{C}^1 \} $.  
Let $f^*(\mathbf{x}) = \sum_{k=1}^p f^*_k(x_k)$ be the population risk
minimizer in $\mathcal{C}_1^p$, 
\begin{equation}
f^* \equiv \arg\min_{f \in \mathcal{C}_1^p} \E\big(f_0(X) - f^*(X)
\big)^2.
\end{equation}
Similarly, we define $\mh \mathcal{C}^1$ as the set of univariate concave functions supported on $[-b, b]$ and define
\begin{equation}
g^*_k = \arg\min_{g_k \in \mh \mathcal{C}^1} \E \big( f_0(X) - f^*(X)
- g_k(X_k) \big)^2.
\end{equation}
We let $S = \{ k = 1,\ldots,p \,:\, f^*_k \neq 0 \trm{ or } g^*_k \neq 0\}$ and let $s = |S|$. By additive faithfulness (Theorem~\ref{thm:acdc_faithful}), it must be that $S_0 \subset S$ and thus $s \geq s_0$. In some cases such as when $X_{S_0}, X_{S^c_0}$ are independent, we have $S = S_0$.
Each of our theorems will use a subset of the following assumptions:
\begin{packed_enum}
\item[A1:] $X_S, X_{S^c}$ are independent. 
\item[A2:] $f_0$ is convex and twice-differentiable. 
\item[A3:] $\|f_0\|_\infty \leq sB$ and $\| f^*_k \|_\infty \leq B$ for all $k$.
\item[A4:] $W$ is mean-zero sub-Gaussian, independent of $X$, with scale $\sigma$; i.e., for all $t \in \R$, $\E e^{t \epsilon} \leq e^{\sigma^2 t^2 / 2}$.
\end{packed_enum}
By assumption A1, $f^*_k$ is must be zero for $k\notin S$.
We define $\alpha_{+}, \alpha_{-}$ as a measure of the signal strength of the weakest variable:
\begin{align}
\alpha_{+} &= \inf_{f \in \mathcal{C}_1^p \,:\, \exists k ,\, f^*_k \neq 0 \,\wedge\, f_k = 0} 
       \Big\{ \mathbb{E} \big( f_0(X) - f(X) \big)^2 - 
        \mathbb{E} \big( f_0(X) - f^*(X) \big)^2  \Big\} \label{eqn:signal_level_defn} \\
\alpha_{-} &=   \min_{k \in S \,:\, g^*_k \neq 0}
      \Big\{ \mathbb{E} \big( f_0(X) - f^*(X) \big)^2 - 
    \mathbb{E} \big( f_0(X) - f^*(X) - g^*_k(X_k) \big)^2 \Big\} \nonumber
\end{align}
These quantities play the role of the absolute value of the smallest nonzero
coefficient in the true linear model in lasso theory.  Intuitively, if
$\alpha_{+}$ is small, then it is easier to make a false omission in the
additive convex stage of the procedure. If $\alpha_{-}$ is small, then
it is easier to make a false omission in the decoupled concave stage
of the procedure.

@@

\begin{theorem}[Controlling false positives]
\label{thm:false_positive}
Suppose assumptions A1-A4 hold. Define $\tilde{\sigma} \equiv \max(\sigma, B)$,
and suppose 
\begin{equation}
\lambda_n \geq 8 s \tilde{\sigma}  \sqrt{ \frac{\log^2 np}{n}}.
\end{equation}  
Then with probability at least $ 1 - \frac{12}{np}$, for all $k \in
S^c$, and for all $i'=1,\ldots, n$,
\begin{equation}
\Big| \frac{1}{2n}\hat{r}^\tran \mathbf{1}_{(i':n)_k} \Big| < \lambda_n
\end{equation}
and for all $k \in S^c$, both the AC solution $\hat{f}_k$ from optimization~\eqref{opt:alternate_opt} and the DC solution $\hat{g}_k$ from optimization~\eqref{opt:alternate_opt_concave} are zero. 
\end{theorem}

@@

\begin{theorem}[Controlling false negatives]
\label{thm:false_negative}
Suppose assumptions A1-A4 hold. Let $\hat{f}$ be any AC solution to
the restricted regression with $B$-boundedness constraint, and let
$\hat{g}_k$ be any DC solution to the restricted regression with
$B$-boundedness constraint. Let $\tilde{\sigma}$ denote $\max(\sigma,
B)$.  Suppose 
\begin{equation}
\lambda_n \leq 9 s \tilde{\sigma} \sqrt{\frac{1}{n} \log^2 np}
\end{equation}
and that $n$ is sufficiently large so that 
\begin{equation}
\frac{n^{4/5}}{\log np} \geq B^4 \tilde{\sigma}^2 s^5.
\end{equation}
Assume that the signal-to-noise ratio satisfies
\begin{align}
\frac{\alpha_{+}}{\tilde{\sigma}} & \geq c B^2
\sqrt{\frac{s^5}{n^{4/5}} \log^2 np}\\
\frac{\alpha_{-}^2}{\tilde{\sigma}} &\geq c B^2
\sqrt{\frac{s^5}{n^{4/5}} \log^2 np}
\end{align}
where $c$ is a constant.  Then with probability at least $1 -
\frac{C}{n}$ for some constant $C$, 
$\hat{f}_k \neq 0$ or $\hat{g}_k \neq 0$ 
for all $k \in S$.
\end{theorem}

This is a finite sample version of
Theorem~\ref{thm:convex_faithful}. We need stronger assumptions in
Theorem~\ref{thm:false_negative} to use our additive faithfulness
result, Theorem~\ref{thm:convex_faithful}. We also include an extra
boundedness constraint so that we can use recent bracketing number
results \cite{kim2014global}. The full proof of Theorem~\ref{thm:false_negative} is in Section~\ref{sec:false_negative_proof} of the appendix.

@@

\end{corollary}
The above corollary implies that sparsistency is achievable at the
same exponential scaling of the ambient dimension scaling attained
with parametric models, $p = O(\exp(n^c))$ for $c<1$.  The cost of
nonparametric modeling through shape constraints 
is reflected in the scaling with respect to
the number of relevant variables, which can scale as $s = o(n^{4/25})$.
